Digital economy in the UK: a multi-scalar story of the diffusion of web technologies

### 2023-03-21 Untitled/Untitled.Rmd
paper first draft

---
title: Title of submission to PLOS journal
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    corresponding: e.tranos@bristol.ac.uk
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
abstract: |
  blah blah

author_summary: |
  blah blah
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
header-includes:
- \usepackage{rotating, graphicx, dcolumn, booktabs, caption, xcolor}
editor_options: 
  markdown: 
    wrap: 72
---

```{r echo=FALSE, message = FALSE, warning=FALSE}
library(stargazer)
library(tidyverse)
#library(rmarkdown)
```

# Introduction {#sec:1}

@beardsell1999spatial To characterize evolution of the computer
industry, we examine the distribution of relative employment across
cities in 1977 and how that distribution changes over time to 1992

@@

larger local technological niches (at least from a demand perspective)
are more likely to be formed in urban areas than in rural ones, which is
in line with the work of Ha¨gerstrand (1965a,b). However, size is not
the only regional characteristic that may matter in this context.
Regions also differ in accumulated experiences and the presence of tacit
knowledge with respect to products, as well as in actors' propensity
share this knowledge among producers (Martin et al., 2019)

@bento2015spatial The concept of absorptive capacity has also been
applied in the TIS context in terms of the con-struction of capacity
needed to transfer and implement a new technology in the receiving
country (cf.Van Alphen, 2011), with repercussions for the nature of
system functions

@das2022diffusion [not good paper] Invention, innovation and diffusion
are considered as the three pillars of the theory of technological
change and Schumpeter is considered as the father of the study of
diffusion

Epidemic approach: The approach emphasizes that the adoption of a
technology spreads like an infection among the potential adopters. By
taking a homogeneous group of potential adopters as an assumption, it
explains the adoption of any innovation.

Rogers3, that divides adopters as: (I.) Innovators: first 2.5%, (II.)
Early adopters: next 13.5%, (III.) Early Majority: following 34%, (IV.)
Late Majority: next 34%, and the rest as (V.) Laggards

Contagious diffusion=\> spatial autocorelation

the three geographic diffusion processes are (1) purely contagious where
distance or adjacency is the absolute controlling factor, (2) purely
hierarchical where size or urban position in the central place hierarchy
is the absolute controlling factor, or (3) where the location of change
is purely random. These are the pure or ideal forms of the diffusion
process; all real diffusion processes are the result of a combination of
these extremes.

@@

Diffusion is a spatial (Hagerstrand, 1967) as well as a temporal
process, and historical evidence confirms that technologies diffuse at
different times, at different rates, and to different extents in
different places, and can be significantly influenced by policies
(Victor, 1993). An illustrative empirically based theory for technology
diffusion acrossmultiple regions is suggested by "Schmidt's Law"
(Grubler, 1990). With respect to a specific technology, it divides
regions into three groups: core, rim, and periphery. The core iswhere
the technology is invented, subject to experimentation, and first
deployed commercially. To develop the technology, the core must have
both sufficient innovative ability and economic motivation to make the
necessary resource commitment. As the technology spreads from the core
to the rim and eventually to the periphery, later adopters have the
advantage of benefiting from the experiences of earlier adopters via
knowledge spillover effects (Verdolini and Galeotti, 2011). At this
point, the technology has likely been refined and costs have likely
declined significantly. Schmidt's Law claims that, as a result,
diffusion proceeds at a faster rate in regions which adopt the
technology later. However, diffusion tends to be less pervasive in
regions where adoption is delayed, ultimately saturating at a lower
extent than in regions where adoption occurred earlier. This is often
attributed to a lack of proper institutions and infrastructures in later
adopters, markets whichmay not be as favorable to a technology, or the
availability of yet newer options that invite technological
leapfrogging.

Empirical evidence supports the validity of Schmidt's Law over a wide
range of technologies, time periods, and geographical contexts. A recent
meta-analysis of technology up-scaling found that diffusion accelerated
moving from the core to the rim and periphery for technologies as
diverse as natural gas power, oil refineries, and automobiles (Wilson,
2009). One historical example that conforms particularly well to
Schmidt's Law is the diffusion of coal power in Europe (Grubler, 2012).
England emerged as the core region for coal power because it had legal
and economic institutions that incentivized scientific pursuits,
domestic coal reserves, and a clear industrial motivation to replace
water power with coal. ...

@wilson201281 Logistic growth describes an initial period of gradual
diffusion as a technology is introduced as a new commercial application,
moving then through a rapid, exponential growth phase, before slowing
and eventually saturating [@grubler1999dynamics]. The substitution of
incumbent technologies by new competitors leads to subsequent decline
and eventual obsolescence.

Early on in their lifecycle, new technologies are crude, imperfect, and
expensive (Rosenberg, 1994). New energy technologies are attractive for
their ability to perform a particular task or deliver a new or improved
energy service (Fouquet, 2010). This is often circumscribed by a
particular set of needs in a particular context: a market 'niche'.
End-users in niche markets are generally less sensitive to the effective
price of the energy service provided or have a higher willingness to pay
for its performance advantages (Fouquet, 2010). Thus initially,
performance dominates cost competitiveness (Wilson and Grubler, 2011).
Market niches afford some protection from competitive pressures,
allowing technologies to be tested and improved in applied settings,
reducing uncertainties with performance or market demand (Kemp et al.,
1998). Costs may only fall substantively after an extended period of
commercial experimentation, concurrent with the establishment of an
industrial base and characteristic moves towards standardisation and
mass production (Grubler, 1998). The influence of accumulating
production experience on costs is captured by the concept of learning.

@grubler1990rise Following the definition given by Rogers, 1983,
diffusion is the process by which an innovation is communicated through
certain communication channels over time among the members of a social
system. An innovation may be an idea, object or practice which is
perceived as new by an individual or another unit of adoption (e.g., an
organization) . Communication via communication channels refers to how
knowledge about an innovation is transferred between the members of a
social system. Communication takes time, and is therefore an important
aspect of innovation diffusion. In fact, all theoretical and empirical
diffusion studies agree that an innovation does not instantly diffuse
into a social system. Instead a typical time pattern of diffusion along
a S-shaped trajectory seems to be the rule. The S-shaped pattern of
diffusion appears to be a basic anthropologic phenomenon, as it is also
confirmed by a large number of studies· of primitive preindustrial
societies.

The scale of spatial innovation diffusion is similar\* to that of
temporal diffusion models: hierarchically decomposed.

Spatial innovation diffusion in Hagerstrand's model consists of three
stages. Stage 1: Local concentrations of initial acceptances (initial
agglomeration) . Stage 2: Radial dissemination outward from the initial
agglomeration, accompanied by the rise of secondary agglomerations.
Stage 3: The condensing and saturation stage, in which filling-in occurs
and diffusion eventually ceases.

Thus, three main characteristics define the spatial diffusion process:
(1) As in temporal diffusion models, an S-shaped pattern in the
cumulative level of adoption. (2) A "hierarchy effect" by which
diffusion proceeds from initial centers to secondary ones. Within the
context of urban systems (central places) this implies a hierarchical
spread of an innovation from larger to smaller centers, and from the
centers to the surrounding hinterland. (3) A "neighborhood effect" Le.,
diffusion proceeds outwards from innovation centers, first "hitting"
(Brown, 1981) nearby rather than far-away locations.

Later Hagerstrand conceptualized physical "barrier" effects like lakes
or uninhabited areas, which, in addition to distance, act as further
retarding effects on diffusion. These are formalized in the form of
"zero" or "half" contact multiplicators on the (distance decaying)
message flows.

With respect to the formalization of the communication flows Hagerstrand
defines a "mean information field" (MIF), in which the probability of
communication is a negative function of distance between individuals

@@

Rogers (1995) characterized early adopters as knowledgeable risk takers.
Griliches (1957) looked at the rate of return for early adopters and
characterized them as profit maximizers. The geographer Hagerstrand
(1967) was focusing on the character of early adopters in the
transmittal process that produces follow-on participants in the process.
Space was treated as a contiguity system with embedded characteristics
producing barrier elements to the diffusion process.

REVIEW ON Technological Diffusion

Perkins and Neumayer (2005) examined whether latecomers have a higher
diffusion rate of three technologies including digital telephone
mainline

@@

Hagerstrand (1968) was the first to demonstrate that diffusion typically
starts from innovative centers ('core´) and disseminates, through a
hierarchy of subcenters, to the periphery. This process is sequential
rather than simultaneous, and tends to accelerate from core to
periphery, where diffusion reaches a lower intensity than in the core
(Hagerstrand, 1968; Grubler, 1990; Morrill, 2005). A similar effect of
spatial acceleration has been identified in marketing research and is
known as the "lead-lag effect" (Peres et al., 2010).

Geographers, of course, were at the forefront of quantitative diffusion
research. Ha¨gerstrand's (1967) early work on understanding innovation
diffusion in Sweden using simulation modeling is particularly noteworthy
in this respect. However, already long before the ''cultural turn'' in
economic geography (Barnes 2001), geographers' interest in formally
modeling the diffusion of new innovations waned (Gregory 1985). Indeed,
much of the recent quantitative research into the diffusion of new
technology has been undertaken by economists, sociologists, and business
scholars.

Theoretical models disagree as to why firms adopt innovations at
different times. Epidemic models emphasize information (Griliches 1957).
Certain firms are hypothesized to adopt earlier because they come into
contact with, and learn from, adopters of the new technology before
others. Economic models, on the other hand, predominantly emphasize firm
heterogeneity (Ireland and Stoneman 1986). Firms adopt technologies at
different times because they differ with respect to various
organizational and environmental variables influencing the economic
returns from adoption (Blackman 1999).

@meade2021modelling There are numerous agents who would benefit from
accurate predictions of introduction times. These include: suppliers of
network equipment for production planning; suppliers of mobile phones
who need to have inventories of appropriately configured handsets;
international network planners who need to provide sufficient bandwidth
for communications between different countries; network operators and
regulatory authorities.

@fritsch2015new

Hägerstrand (1952, 1967) was the first scholar to intensively analyze
spatial diffusion pro cesses. Based on the empirical observations of the
regional spread of process innovations, he hypothesized that new
technology is first implemented in the 'center' -- the large agglom
erations -- and then moves 'down' the spatial hierarchy, the last stop
being the 'periphery', i.e. remote and sparsely populated regions. There
are at least two factors that may explain this pattern: first, the
transfer of tacit knowledge via face-to-face contact and second, the
absorptive capacity of a region.

# Literature review {\#sec2} MAYBE SKIP THIS??

@@

## Multi-country analysis {#sec3.1}

>>>>

---
title: Digital economy in the UK: a multi-scalar story of the diffusion of web technologies
author:
  - name: Emmanouil Tranos
    email: e.tranos@bristol.ac.uk
    affiliation: University of Bristol and The Alan Turing Institute
    correspondingauthor: true
    footnote: 1
address:
  - code: University of Bristol and The Alan Turing Institute
    address: University of Bristol, School of Geographical Sciences, Bristol, UK; The Alan Turing Institute, London, UK
footnote:
  - code: 1
    text: "This is the first author footnote."
  - code: 2
    text: "Another author footnote."
abstract: |
  This paper maps the participation in the digital economy and its evolution in the UK over space and time. Most of the existing economic geography literature which dealt with the spatiality of the internet employed supply-side measures, such as infrastructural capacity, in order to understand the geography of the digital economy and its potential spatial economic effects. Useful as these approaches might have been, they cannot capture the micro-processes and the characteristics of the individual online behaviour. Using large volumes of archived and geolocated web content, this paper models the diffusion of web technologies over space and time in the UK. The data and geolocation strategy allow to capture these processes at a very granular spatial scale. The modelling approach, which is based on simple spatial analytical methods and on the estimation of diffusion curves at various scales, enables to depict the role of geography and other cognitive factors which drove the diffusion of web technologies. Although the focus is on a recent historical period -- 1996-2012 -- the results of the analysis depict diffusion mechanisms which can be very useful in understanding the evolutionary patterns of the adoption of other newer technologies.

keywords: 
  - keyword1
  - keyword2
journal: "An awesome journal"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: mybibfile.bib
linenumbers: false
numbersections: true
# Use a CSL with `citation_package = "default"`
# csl: https://www.zotero.org/styles/elsevier-harvard
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: natbib
---
# Introduction {#sec:1}

Geographers were always interested in how new technologies and innovations diffuse across space and, importantly, how such spatio-temporal processes can be modelled. The seminal contribution of @hagerstrand1968innovation is illustrative of this early interest. However, the torch of exploring and modelling such processes had been passed to other disciplines such as economics, business studies and sociology well before the 'cultural turn' of economic geography [@perkins2005international]. A potential explanation of lack of studies exploring the diffusion of new and, more specifically, digital technologies across *both* space and time can be attributed to the scarcity of relevant and granular enough data. As @zook2022mapping highlight, digital activities are hardly ever captured in official data.

This paper aims to reinstate geographers' interest in how new and digital technologies diffuse over space and time. It adopts a geographic standpoint to explore and map the diffusion of web technologies in the UK over space and time. It does so by employing a novel source of big data which captures the active engagement with web technologies during the $1996-2013$ period.

The motivation for this paper lies in the fact that there are various stakeholders who are interested in knowing how new digital technologies diffused over space and time use this information to make predictions regarding the diffusion of related future technologies. As per @meade2021modelling a variety of actors have a direct interest in gaining such knowledge including network equipment suppliers; network operators, regulatory and local authorities. And despite the spatial heterogeneity of such diffusion mechanisms and the policy relevance, there are very limited attempts in the literature to analyse the diffusion of new digital technologies at a granular level.

the paper answers an empirical question: how did a

<!-- motivation -->

@fritsch2015new
Hägerstrand (1952, 1967) was the first scholar to intensively analyze
spatial diffusion pro cesses. Based on the empirical observations of the
regional spread of process innovations, he hypothesized that new
technology is first implemented in the 'center' -- the large agglom
erations -- and then moves 'down' the spatial hierarchy, the last stop
being the 'periphery', i.e. remote and sparsely populated regions. There
are at least two factors that may explain this pattern: first, the
transfer of tacit knowledge via face-to-face contact and second, the
absorptive capacity of a region.

<!-- key concepts -->
@bento2015spatial The concept of absorptive capacity has also been
applied in the TIS context in terms of the con-struction of capacity
needed to transfer and implement a new technology in the receiving
country (cf.Van Alphen, 2011), with repercussions for the nature of
system functions

@bednarz2020pulled 
larger local technological niches (at least from a demand perspective)
are more likely to be formed in urban areas than in rural ones, which is
in line with the work of Ha¨gerstrand (1965a,b). However, size is not
the only regional characteristic that may matter in this context.
Regions also differ in accumulated experiences and the presence of tacit
knowledge with respect to products, as well as in actors' propensity
share this knowledge among producers (Martin et al., 2019)

<!-- @das2022diffusion -->
<!-- Epidemic approach: The approach emphasizes that the adoption of a -->
<!-- technology spreads like an infection among the potential adopters. By -->
<!-- taking a homogeneous group of potential adopters as an assumption, it -->
<!-- explains the adoption of any innovation. -->

<!-- Rogers3, that divides adopters as: (I.) Innovators: first 2.5%, (II.) -->
<!-- Early adopters: next 13.5%, (III.) Early Majority: following 34%, (IV.) -->
<!-- Late Majority: next 34%, and the rest as (V.) Laggards -->

Contagious diffusion=> spatial autocorelation

<!-- the three geographic diffusion processes are (1) purely contagious where -->
<!-- distance or adjacency is the absolute controlling factor, (2) purely -->
<!-- hierarchical where size or urban position in the central place hierarchy -->
<!-- is the absolute controlling factor, or (3) where the location of change -->
<!-- is purely random. These are the pure or ideal forms of the diffusion -->
<!-- process; all real diffusion processes are the result of a combination of -->
<!-- these extremes. -->

<!-- @das2022diffusion [not good paper] Invention, innovation and diffusion -->
<!-- are considered as the three pillars of the theory of technological -->
<!-- change and Schumpeter is considered as the father of the study of -->
<!-- diffusion -->

@leibowicz2016representing
Diffusion is a spatial (Hagerstrand, 1967) as well as a temporal
process, and historical evidence confirms that technologies diffuse at
different times, at different rates, and to different extents in
different places, and can be significantly influenced by policies
(Victor, 1993).

<!-- @leibowicz2016representing -->
<!-- An illustrative empirically based theory for technology -->
<!-- diffusion across multiple regions is suggested by "Schmidt's Law" -->
<!-- (Grubler, 1990). With respect to a specific technology, it divides -->
<!-- regions into three groups: core, rim, and periphery. The core is where -->
<!-- the technology is invented, subject to experimentation, and first -->
<!-- deployed commercially. To develop the technology, the core must have -->
<!-- both sufficient innovative ability and economic motivation to make the -->
<!-- necessary resource commitment. As the technology spreads from the core -->
<!-- to the rim and eventually to the periphery, later adopters have the -->
<!-- advantage of benefiting from the experiences of earlier adopters via -->
<!-- knowledge spillover effects (Verdolini and Galeotti, 2011). At this -->
<!-- point, the technology has likely been refined and costs have likely -->
<!-- declined significantly. Schmidt's Law claims that, as a result, -->
<!-- diffusion proceeds at a faster rate in regions which adopt the -->
<!-- technology later. However, diffusion tends to be less pervasive in -->
<!-- regions where adoption is delayed, ultimately saturating at a lower -->
<!-- extent than in regions where adoption occurred earlier. This is often -->
<!-- attributed to a lack of proper institutions and infrastructures in later -->
<!-- adopters, markets whichmay not be as favorable to a technology, or the -->
<!-- availability of yet newer options that invite technological -->
<!-- leapfrogging. -->

wilson201281 Early on in their lifecycle, new technologies are crude, imperfect, and
expensive (Rosenberg, 1994). New energy technologies are attractive for
their ability to perform a particular task or deliver a new or improved
energy service (Fouquet, 2010). This is often circumscribed by a
particular set of needs in a particular context: a market 'niche'.
End-users in niche markets are generally less sensitive to the effective
price of the energy service provided or have a higher willingness to pay
for its performance advantages (Fouquet, 2010). Thus initially,
performance dominates cost competitiveness (Wilson and Grubler, 2011).
Market niches afford some protection from competitive pressures,
allowing technologies to be tested and improved in applied settings,
reducing uncertainties with performance or market demand (Kemp et al.,
1998). Costs may only fall substantively after an extended period of
commercial experimentation, concurrent with the establishment of an
industrial base and characteristic moves towards standardisation and
mass production (Grubler, 1998). The influence of accumulating
production experience on costs is captured by the concept of learning.

<!-- @grubler1990rise Following the definition given by Rogers, 1983, -->
<!-- diffusion is the process by which an innovation is communicated through -->
<!-- certain communication channels over time among the members of a social -->
<!-- system. An innovation may be an idea, object or practice which is -->
<!-- perceived as new by an individual or another unit of adoption (e.g., an -->
<!-- organization) . Communication via communication channels refers to how -->
<!-- knowledge about an innovation is transferred between the members of a -->
<!-- social system. Communication takes time, and is therefore an important -->
<!-- aspect of innovation diffusion. In fact, all theoretical and empirical -->
<!-- diffusion studies agree that an innovation does not instantly diffuse -->
<!-- into a social system. Instead a typical time pattern of diffusion along -->
<!-- a S-shaped trajectory seems to be the rule. The S-shaped pattern of -->
<!-- diffusion appears to be a basic anthropologic phenomenon, as it is also -->
<!-- confirmed by a large number of studies· of primitive preindustrial -->
<!-- societies. -->

grubler1990rise
The scale of spatial innovation diffusion is similar to that of
temporal diffusion models: hierarchically decomposed.

<!-- grubler1990rise -->
<!-- Spatial innovation diffusion in Hagerstrand's model consists of three -->
<!-- stages. Stage 1: Local concentrations of initial acceptances (initial -->
<!-- agglomeration) . Stage 2: Radial dissemination outward from the initial -->
<!-- agglomeration, accompanied by the rise of secondary agglomerations. -->
<!-- Stage 3: The condensing and saturation stage, in which filling-in occurs -->
<!-- and diffusion eventually ceases. -->

<!-- grubler1990rise -->
<!-- Thus, three main characteristics define the spatial diffusion process: -->
<!-- (1) As in temporal diffusion models, an S-shaped pattern in the -->
<!-- cumulative level of adoption. (2) A "hierarchy effect" by which -->
<!-- diffusion proceeds from initial centers to secondary ones. Within the -->
<!-- context of urban systems (central places) this implies a hierarchical -->
<!-- spread of an innovation from larger to smaller centers, and from the -->
<!-- centers to the surrounding hinterland. (3) A "neighborhood effect" Le., -->
<!-- diffusion proceeds outwards from innovation centers, first "hitting" -->
<!-- (Brown, 1981) nearby rather than far-away locations. -->

@grubler1990rise
Later Hagerstrand conceptualized physical "barrier" effects like lakes
or uninhabited areas, which, in addition to distance, act as further
retarding effects on diffusion. These are formalized in the form of
"zero" or "half" contact multiplicators on the (distance decaying)
message flows.

@grubler1990rise
With respect to the formalization of the communication flows Hagerstrand
defines a "mean information field" (MIF), in which the probability of
communication is a negative function of distance between individuals

@perkins2005international
Theoretical models disagree as to why firms adopt innovations at
different times. Epidemic models emphasize information (Griliches 1957).
Certain firms are hypothesized to adopt earlier because they come into
contact with, and learn from, adopters of the new technology before
others. Economic models, on the other hand, predominantly emphasize firm
heterogeneity (Ireland and Stoneman 1986). Firms adopt technologies at
different times because they differ with respect to various
organizational and environmental variables influencing the economic
returns from adoption (Blackman 1999).

@ding2010modeling Rogers (1995) characterized early adopters as knowledgeable risk takers.
Griliches (1957) looked at the rate of return for early adopters and
characterized them as profit maximizers. The geographer Hagerstrand
(1967) was focusing on the character of early adopters in the
transmittal process that produces follow-on participants in the process.
Space was treated as a contiguity system with embedded characteristics
producing barrier elements to the diffusion process.

@ding2010modeling
REVIEW ON Technological Diffusion

<!-- Hagerstrand (1968) was the first to demonstrate that diffusion typically -->
<!-- starts from innovative centers ('core´) and disseminates, through a -->
<!-- hierarchy of subcenters, to the periphery. This process is sequential -->
<!-- rather than simultaneous, and tends to accelerate from core to -->
<!-- periphery, where diffusion reaches a lower intensity than in the core -->
<!-- (Hagerstrand, 1968; Grubler, 1990; Morrill, 2005). A similar effect of -->
<!-- spatial acceleration has been identified in marketing research and is -->
<!-- known as the "lead-lag effect" (Peres et al., 2010). -->

<!-- methods -->
@wilson201281 Logistic growth describes an initial period of gradual
diffusion as a technology is introduced as a new commercial application,
moving then through a rapid, exponential growth phase, before slowing
and eventually saturating [@grubler1999dynamics]. The substitution of
incumbent technologies by new competitors leads to subsequent decline
and eventual obsolescence.

# Literature review {#sec2} MAYBE SKIP THIS??

<!-- previous studies -->
@beardsell1999spatial To characterize evolution of the computer
industry, we examine the distribution of relative employment across
cities in 1977 and how that distribution changes over time to 1992

@@

@perkins2011internet

@PAPAGIANNIDIS2015308

@@

@leibowicz2016representing
Empirical evidence supports the validity of Schmidt's Law over a wide
range of technologies, time periods, and geographical contexts. A recent
meta-analysis of technology up-scaling found that diffusion accelerated
moving from the core to the rim and periphery for technologies as
diverse as natural gas power, oil refineries, and automobiles (Wilson,
2009). One historical example that conforms particularly well to
Schmidt's Law is the diffusion of coal power in Europe (Grubler, 2012).
England emerged as the core region for coal power because it had legal
and economic institutions that incentivized scientific pursuits,
domestic coal reserves, and a clear industrial motivation to replace
water power with coal. ...

@@

@@

@@

## Results {#sec3.1}

Hexagon density maps: reflect the spatial structure of Britain. Websites
are associated in places where people live and work.

**TODO** maps at the local authority level per firms and discuss
patterns

Neighbourhood effect: diffusion proceeds outwards from innovation
centers, first "hitting" nearby rather than far-away locations (Grubler
1990)

-   Moran's I: for OA and LAD over time **TODO** add 0s

-   LISA maps: for OA and LAD over time More and less expected clusters.
    Different scales show different results

-   Website density regressions: for OA and LAD over time **TODO** add
    0s Similar pattern

Hierarchy effect: from main centers to secondary ones -- central places

-   Gini coefficient. Almost perfect polarisation of web adoption in the
    early stages at a granular level More equally diffused at the Local
    Authority level Plateau overtime

S-shaped diffusion curves

-   S for LADs per firm and OA. **TODO**: OA per firm? fix firms over
    time.

-   Fast and slow LAs map. There is clustering

-   **TODo** check s_uk_firm_11

-   ranks: there is stability and movement
